---
title: "SnehalHw5"
author: "Snehal"
date: "2023-03-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
``{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
```{r}
nrow(choco)
```
```{r}

library(ggplot2)

ggplot(choco, aes(x = Review.Date)) +
  geom_bar()
```
```{r}
library(ggplot2)

ggplot(choco, aes(x = Rating)) +
  geom_histogram(binwidth = 0.25, fill = "dodgerblue", color = "black") +
  ggtitle("Distribution of Chocolate Ratings") +
  xlab("Rating") +
  ylab("Count")

```

```{r}
library(ggplot2)

# Filter data to top 3 locations
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

# Create a boxplot of Rating by Company.Location
ggplot(top3, aes(x = Company.Location, y = Rating)) +
  geom_boxplot(fill = "dodgerblue", color = "black") +
  ggtitle("Distribution of Chocolate Ratings by Company Location") +
  xlab("Company Location") +
  ylab("Rating")

```
```{r}
library(ggplot2)

ggplot(choco, aes(x = Cocoa.Pct, y = Rating)) +
  geom_point(alpha = 0.5, color = "dodgerblue") +
  ggtitle("Rating vs. Cocoa Percentage") +
  xlab("Cocoa Percentage") +
  ylab("Rating")

```

